The Revisited Hidden Weight Bit Function

### 2025-07-29 RevisedHiddenWeight.tex
Acknowledgment
Minor

Since $f$ is the sum of a quadratic function and a weightwise affine function, it is a weightwise quadratic function. Note that, while the \hwbf{} can be computed by first computing the Hamming weight of the input and then applying a linear function, the revisited \hwbf{} can be computed by first computing the Hamming weight of the input and then applying a quadratic function, leading to a similar computational cost to for both.

@@

\ifnum\anon=0
	\section{Acknowledgments}
	Pierrick Méaux was funded by the European Research Council (\textsf{ERC}) under the Advanced Grant program (reference number: 787390). Tim Seuré acknowledges the support of the Luxembourgish “Fonds National de la Recherche” (\textsf{FNR}) through an Individual Grant (reference number: 17936291).
\fi

>>>>

Since $f$ is the sum of a quadratic function and a weightwise affine function, it is a weightwise quadratic function. Note that, while the \hwbf{} can be computed by first computing the Hamming weight of the input and then applying a linear function, the revisited \hwbf{} can be computed by first computing the Hamming weight of the input and then applying a quadratic function, leading to a similar computational cost for both.

@@

\ifnum\anon=0
	\section{Acknowledgments}
	Pierrick Méaux was funded by the European Research Council (\textsf{ERC}) under the Advanced Grant program (reference number: 787390). Tim Seuré acknowledges the support of the Luxembourgish “Fonds National de la Recherche” (\textsf{FNR}) through an Individual Grant (reference number: 17936291). The work of Deng Tang was supported in part by the National Natural Science Foundation of China (\textsf{NSFC}, reference number: 62272303). We would also like to thank Claude Carlet for discussing the function introduced in this work with Deng Tang some years ago.
\fi
